---
title: "Study of Video Games"
author: "Jimmy Yang, Gordon Tran, Kaia Armas"
date: "11/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../source/source.R")
```

# Summary
In our project, we will deal with three different datasets, the steam game dataset, the world game sales dataset, and the world happiness dataset.

The steam dataset ([source](https://www.kaggle.com/datasets/nikdavis/steam-store-games?select=steam.csv)) has `r summary_info$steam_num_observations` observations and `r summary_info$steam_num_variables` variables. The dataset covers most of the games from `r summary_info$steam_min_date` to `r summary_info$steam_max_date`. This data also shows the information about each game, such as the number of positive and negative ratings and average playtime.

The game sales dataset ([source](https://www.kaggle.com/datasets/rush4ratio/video-game-sales-with-ratings)) has  `r summary_info$GS_observations` observations and `r summary_info$GS_variables` variables. It covers `r summary_info$GS_platform_num` platforms and `r summary_info$GS_observations` games from `r summary_info$sale_min_date` to `r summary_info$sale_max_date`. This dataset is about game sales, it contains information on game sales around the different regions for each game; the author separates the region into North America, European Union, Japan, and others. The dataset also has other information about each game, such as the ESRB ratings and Genre.

The world happiness dataset  ([source](https://worldhappiness.report/ed/2019/)) contains the happiness score for `r summary_info$happy_observations` countries in 2019 and other scores that will impact the happiness score. Through out all `r summary_info$happy_observations` countries, `r summary_info$happies_country` is the country with the highest happiness score at `r summary_info$happies_score` and the most unhappy country is `r summary_info$unhappy_country`, with the score of `r summary_info$unhappy_score`

We are planning to use those datasets to help people find the best game that fit their interest and find out the connection bewteen the world happiness score with the game sale on different region.


# Map
```{r happiness_map, echo = FALSE}

happiness_map

```

```{r le_map, echo = FALSE}

revenue_map
```

I decide to use maps to visualize the relationship between video games and happiness scores because both datasets include data for countries in the world; I think maps can give a better view of the comparison than other types of visualization. Both maps have some countries with no color due to the missing data, especially Africa. Still, in North America, Asia, and Australia, we can find some connection between video games and happiness scores. In the North American area, we can see that all the countries have a pretty high happiness score, and USA and Canada have a high amounts of money spent on video games per capita too. This also shows in Australia, where high happiness scores and a high amount of money spent on video games per capita. On the other hand, the Asia area, except Japan, has a pretty low amount of money spent on video games per capita with a pretty low happiness score. This shows that happiness scores and video games have some connection; countries with higher video game revenues will often have a higher happiness score.
